---
title: "Portfolio 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pacman)
p_load(readr, lme4, DHARMa, MuMIn, knitr, kableExtra, tidyverse, ggpubr, ggrepel, grid, jpeg)
ggplot2::theme_set(theme_bw())

```

#PREPROSSESING

Loading in the data and making everything within the right coordinates

```{r cars}

Samples <- read_csv("Exported_EyeLink_data/Samples_merged.csv", col_types = cols(
  ParticipantID = col_character(),
  ParticipantGender = col_character(),
  EyeTracked = col_character(),
  Task = col_character(),
  SearchOrder = col_double(),
  ForagingType = col_character(),
  Trial = col_double(),
  Stimulus = col_character(),
  Video = col_character(),
  Time = col_double(),
  GazeX = col_double(),
  GazeY = col_double(),
  PupilSize = col_double(),
  FixationNo = col_double(),
  Fix_StartTime = col_double(),
  Fix_EndTime = col_double(),
  Fix_Duration = col_double(),
  Fix_MeanX = col_double(),
  Fix_MeanY = col_double(),
  Fix_MeanPupilSize = col_double(),
  SaccadeNo = col_double(),
  Sac_StartTime = col_double(),
  Sac_EndTime = col_double(),
  Sac_Duration = col_double(),
  Sac_StartX = col_double(),
  Sac_StartY = col_double(),
  Sac_EndX = col_double(),
  Sac_EndY = col_double(),
  Sac_PeakVelocity = col_double(),
  Sac_MeanVelocity = col_double(),
  Sac_Blink = col_logical(),
  Sac_Direction = col_character(),
  Sac_Amplitude = col_double()))


Samples <- Samples %>% 
  mutate(GazeY = 1051-GazeY, Fix_MeanY = 1051-Fix_MeanY) %>% 
  filter(Time<=41202)
```

Making a density plot over pupil size

```{r}

pupil_size <- Samples[!is.na(Samples$PupilSize) & Samples$Task == "SocialEngagement",] %>% 
  group_by(ParticipantID, ParticipantGender, Trial, PupilSize, Video) %>% 
  summarize()

ggplot(pupil_size, aes(PupilSize, color = ParticipantGender)) + geom_density() 

```

Adding info

```{r}

Add_Info <- function(df){
  
  df$ActorGender[grepl("f",df$Video)]='Female'
  df$ActorGender[grepl("m",df$Video)]='Male'
  
  df$Direction[grepl("_pl_o1_dir",df$Video)]='Direct'
  df$Direction[grepl("_pl_o1_div",df$Video)]='Averted'
  
  df$Ostention[grepl("_+o",df$Video)]= "Ostensive"
  df$Ostention[grepl("_-o",df$Video)]= "Non-ostensive"
  
  return(df)
}

pupil_size <- Add_Info(pupil_size)

```


```{r}

mLog <-
  glmer(
    PupilSize ~ Direction * Ostention + (1 + Direction * Ostention | ParticipantID),
    family = gaussian(link = "log"),
    data = pupil_size
  )

pm <- predict(mLog)

plot(density(pm))
plot(density(pupil_size$PupilSize))

summary(abs(pm-pupil_size$PupilSize))

```


```{r}

dLog <- simulateResiduals(mLog, n = 250)
plot(dLog)

summary(mLog)
summary(pupil_size$PupilSize)


```


```{r}

r.squaredGLMM(mLog) #We are interested in the R^2m, because it says how much of the variance can be explained by the model, which is not that much, even though the residualse is cute like the expected

```

#vISUALISATION

```{r}

#Making a subset, where we get the mean pupil size, so now we have to data sets, this one contains only one point for each participant, whereas the other contains all the datapoints
Pup <- pupil_size[!is.na(pupil_size$PupilSize),] %>% # remember to remove NAs 
  group_by(ParticipantID, Trial) %>% 
  summarize(PupilSize = mean(PupilSize),
            ParticipantGender = ParticipantGender[1],
            Ostention = Ostention[1],
            Direction = Direction[1])


# plot density of pupil sizes, color by gender
ggplot(Pup, aes(PupilSize, color = ParticipantGender)) + geom_density() + facet_grid(Direction~Ostention)

# plot density of pupil sizes color by participant ID
ggplot(Pup, aes(PupilSize, color = ParticipantID)) + geom_density() + facet_grid(Direction~Ostention)

```

Making a scanpath on top of a ostensive and direct picture (missing a picture of the conditions, so i just copied one from the other cexperiment just so the script ran haha)

```{r}

x = subset(Samples, ParticipantID ==    'F1' & Trial == 3)

## Let's make a summary dataset
Fix <- x[!is.na(x$FixationNo),] %>% 
  group_by(FixationNo) %>% # since I only have one participant and one trial
  summarize(MeanX = Fix_MeanX[1], MeanY = Fix_MeanY[1], Duration = Fix_Duration[1]) %>% 
  filter(Duration>=300) # only keep fixations > 300 ms

img <- jpeg::readJPEG('stimuli_Foraging/space_capsules.jpg')  
img <- grid::rasterGrob(img, width=unit(1, "npc"), height = unit(1,"npc"),
                        interpolate = FALSE)

ggplot(Fix, aes(MeanX, MeanY, color = Fix$FixationNo)) + 
  annotation_custom(img, xmin = 0, xmax = 1680, ymin = 0, ymax = 1050) +
  # hacky way to adjust opacity of background picture:
  annotate(geom = "rect", xmin = 0, xmax = 1680, ymin = 0, ymax = 1050, fill = "white", alpha = .3) +
  geom_path(color = "black") +
  geom_point(size = Fix$Duration*.02, alpha = .8) +
  geom_text_repel(aes(label = Fix$Duration), size = 3, color = "white") +
  xlim(0,1680) + ylim(0,1050)

```


Making a scanpath on top of a non-ostensive and averted picture (missing a picture of the conditions, so i just copied one from the other experiment just so the script ran haha)

```{r}

x_na = subset(Samples, ParticipantID ==    'F2' & Trial == 4)

## Let's make a summary dataset
Fix <- x_na[!is.na(x$FixationNo),] %>% 
  group_by(FixationNo) %>% # since I only have one participant and one trial
  summarize(MeanX = Fix_MeanX[1], MeanY = Fix_MeanY[1], Duration = Fix_Duration[1]) %>% 
  filter(Duration>=300) # only keep fixations > 300 ms

img <- jpeg::readJPEG('stimuli_Foraging/space_capsules.jpg')  
img <- grid::rasterGrob(img, width=unit(1, "npc"), height = unit(1,"npc"),
                        interpolate = FALSE)

ggplot(Fix, aes(MeanX, MeanY, color = Fix$FixationNo)) + 
  annotation_custom(img, xmin = 0, xmax = 1680, ymin = 0, ymax = 1050) +
  # hacky way to adjust opacity of background picture:
  annotate(geom = "rect", xmin = 0, xmax = 1680, ymin = 0, ymax = 1050, fill = "white", alpha = .3) +
  geom_path(color = "black") +
  geom_point(size = Fix$Duration*.02, alpha = .8) +
  geom_text_repel(aes(label = Fix$Duration), size = 3, color = "white") +
  xlim(0,1680) + ylim(0,1050)

```

The total change of pupil size across a trial

```{r}

ggplot(Samples, aes(Time, PupilSize, color = ParticipantGender)) +
  geom_smooth() + facet_wrap(.~Task, scales = "free_x")

```

#ANALYSIS - i have problems here ahah

```{r}

pupil_size_model <- glmer(PupilSize ~ Direction * Ostention + (1 + Direction * Ostention | ParticipantID), family = gaussian(link="log"), data = Pup) 
summary(pupil_size_model)


```

R2m = indicate how much of the variance is explained by the model

```{r}
r.squaredGLMM(pupil_size_model)

```

Spaghetti plot of the pupil size according to condition

```{r}

ggplot(pupil_size, aes(Direction, PupilSize, group = ParticipantID))+
  geom_smooth(method=lm, aes(color=ParticipantID), se=FALSE)+
  theme_classic()+
  xlab("Condition") +
  ylab("Pupil Size") + 
  facet_wrap(.~Ostention)

```

